Unshuffling Permutations

### 2015-09-14 article.tex
notations

\begin{proof}[of Lemma~\ref{lemma:at most one edge monotone}]
  \begin{figure}[t!]
    \centering
    \subfigure[%
      An increasing pattern before and above a decreasing pattern.
    ]{%
      \begin{tikzpicture}
        [
          scale=0.45,
          label/.style={anchor=base}
        ]
        % increasing pattern
        \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,5.8) grid (5.2,11.2);
        \foreach \x/\y in {0/6,1/7,2/8,3/9,4/10,5/11} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % decreasing pattern
        \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,-0.2) grid (11.2,5.2);
        \foreach \x/\y in {6/5,7/4,8/3,9/2,10/1,11/0} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % labels
        \node [label] (a) at (1,5) {$a$};
        \node [label] (b) at (4,5) {$b$};
        \node [label] (ap) at (7,-1) {$a'$};
        \node [label] (bp) at (10,-1) {$b'$};
        \node (nu1) at (2.5,4) {$\sigma_1$};
        \node (nu2) at (8.5,-2) {$\sigma_2$};
        % crossings edges
        \draw [line width=1pt]
        (1,7) .. controls +(0,12) and +(0,10) .. (7,4);
        \draw [line width=1pt]
        (4,10) .. controls +(0,12) and +(0,10) .. (10,1);
      \end{tikzpicture}
      \label{subfig:increasing before and aboce decreasing}
    }% end subfigure
    \qquad
    \subfigure[%
      A decreasing pattern before and below an increasing pattern.
    ]{%
    \begin{tikzpicture}
      [
        scale=0.45,
        label/.style={anchor=base}
      ]
      % decreasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,-0.2) grid (5.2,5.2);
      \foreach \x/\y in {0/5,1/4,2/3,3/2,4/1,5/0} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % decreasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,5.8) grid (11.2,11.2);
      \foreach \x/\y in {6/6,7/7,8/8,9/9,10/10,11/11} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % labels
      \node [label] (a) at (1,-1) {$a$};
      \node [label] (b) at (4,-1) {$b$};
      \node [label] (ap) at (7,5) {$a'$};
      \node [label] (bp) at (10,5) {$b'$};
      \node (nu1) at (2.5,-2) {$\sigma_1$};
      \node (nu2) at (8.5,4) {$\sigma_2$};
      % crossings edges
      \draw [line width=1pt]
      (1,4) .. controls +(0,10) and +(0,12) .. (7,7);
      \draw [line width=1pt]
      (4,1) .. controls +(0,10) and +(0,12) .. (10,10);
      \end{tikzpicture}
      \label{subfig:decresing before and below increasing}
    }% end subfigure
    \caption{\label{fig:subfig:no (nu_1, nu_2)-edge}%
      Lemma~\ref{lemma:at most one edge monotone}:
      Assuming a $(\nu_1,\nu_2)$-edge $(a, b)$ in $\mathcal{M}$.
    }
  \end{figure}
  We first prove \emph{1}.
  Suppose, aiming at a contradiction, that there exist two
  $(\sigma_1, \sigma_2)$-edges $(a, a')$ and $(b, b')$ in $\mathcal{M}$.
  Since $\mathcal{M}$ is containment-free, we may assume $a < b$ and $a' < b'$.
  Therefore, we have
  $\pi(a) < \pi(b)$ (since $\sigma_1$ is increasing) and
  $\pi(a') > \pi(b')$ (since $\sigma_2$ is decreasing),
  which contradicts our hypothesis.

  As for \emph{2}, suppose, still aiming at a contradiction,
  that there exist two
  $(\sigma_1, \sigma_2)$-edges $(a, a')$ and $(b, b')$ in $\mathcal{M}$.
  Since $\mathcal{M}$ is containment-free, we may assume $a < b$ and $a' < b'$.
  Therefore, we have
  $\pi(a) > \pi(b)$ (since $\sigma_1$ is decreasing) and
  $\pi(a') < \pi(b')$ (since $\sigma_2$ is increasing),
  which contradicts our hypothesis.
  \qed
\end{proof}

@@

  \begin{figure}[t!]
    \centering
    \begin{tikzpicture}[
      scale=.95,
      >=stealth',
      shorten >=1pt,
      main node/.style={align=center},
      cell/.style={draw,ultra thick,fill=black!5},
      structure link/.style={line width=1.5pt},
      pattern link/.style={line width=1.5pt,black!20},
      monotone/.style={->,thick}
      ]
      % edges
      % pi 1 - pi 2
      \draw [pattern link] (8.5,6) .. controls +(0,1) and +(0,2) .. (10.5,5);
      % pi 2 - sigma 2
      \draw [pattern link] (10.5,5) .. controls +(0,1) and +(0,3) .. (11.5,4);
      % 1
      \draw [structure link] (0.5,11) .. controls +(0,2) and +(0,1) .. (2.5,12);
      \node (claim edge 1) at (1.5,13) {Claim\ref{}};
      % 2
      \draw [structure link] (1.5,2) .. controls +(0,1) and +(0,3) .. (6.5,1);
      \node (claim edge 1) at (4,3.5) {Claim\ref{}};
      % 3
      \draw [structure link] (3.5,9) .. controls +(0,3) and +(0,1.5) .. (7.5,10);
      \node (claim edge 1) at (5.5,11.5) {Claim\ref{}};
      % 4
      \draw [structure link] (5.5,8) .. controls +(0,1) and +(0,7) .. (9.5,3);
      \node (claim edge 1) at (8.5,8.5) {Claim\ref{}};
      % sigma 1 - pi 1
      \draw [structure link] (4.5,6) .. controls +(0,-2) and +(0,-1) .. (8.5,5);
      \node (claim edge 1) at (6.5,4) {Claim\ref{}};
      % nodes
      % 1
      \draw [cell] (0,10) -- (1,10) -- (1,11) -- (0,11) -- cycle;
      \draw [monotone] (0,10) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu_1$};
      %\draw [draw,ultra thick,fill=black!5] (0,10) -- (1,10) -- (1,11) -- (0,11) -- cycle;
      \draw [cell] (2,11) -- (3,11) -- (3,12) -- (2,12) -- cycle;
      \draw [monotone] (2,11) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu'_1$};
      % 2
      \draw [cell] (1,1) -- (2,1) -- (2,2) -- (1,2) -- cycle;
      \draw [monotone] (1,2) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu_2$};
      \draw [cell] (6,0) -- (7,0) -- (7,1) -- (6,1) -- cycle;
      \draw [monotone] (6,1) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu'_2$};
      % 3
      \draw [cell] (3,8) -- (4,8) -- (4,9) -- (3,9) -- cycle;
      \draw [monotone] (3,8) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu_3$};
      \draw [cell] (7,9) -- (8,9) -- (8,10) -- (7,10) -- cycle;
      \draw [monotone] (7,9) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu'_3$};
      % 4
      \draw [cell] (5,7) -- (6,7) -- (6,8) -- (5,8) -- cycle;
      \draw [monotone] (5,8) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu_4$};
      \draw [cell] (9,2) -- (10,2) -- (10,3) -- (9,3) -- cycle;
      \draw [monotone] (9,3) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu'_4$};
      % sigma 1
      \draw [cell] (4,6) -- (5,6) -- (5,7) -- (4,7) -- cycle;
      \node [main node] (sigma1) at (4.5,6.5) {$\sigma'$};
      % pi 1
      \draw [cell] (8,5) -- (9,5) -- (9,6) -- (8,6) -- cycle;
      \node [main node] (pi1) at (8.5,5.5) {$\pi'$};
      % pi 2
      \draw [cell] (10,4) -- (11,4) -- (11,5) -- (10,5) -- cycle;
      \node [main node] (sigma2) at (10.5,4.5) {$\pi''$};
      % sigma 2
      \draw [cell] (11,3) -- (12,3) -- (12,4) -- (11,4) -- cycle;
      \node [main node] (pi2) at (11.5,3.5) {$\sigma''$};
      % grid
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (0,0) grid (12,12);
      % row size
      \foreach \y/\N in {0.5/N_2,1.5/N_2,2.5/N_4,3.5/k,4.5/n,5.5/n+2,6.5/k+2,7.5/N_4,8.5/N_3,9.5/N_3,10.5/N_1,11.4/N_1} {
          \node at (-0.5,\y) (R\y) {$\N$};
      }
      % column size
      \foreach \x/\N in
      {0.5/N_1,1.5/N_2,2.5/N_1,3.5/N_3,4.5/k+2,5.5/N_4,6.5/N_2,7.5/N_3,8.5/n+2,9.5/N_4,10.5/n,11.5/k} {
          \node at (\x,-0.5) (C\x) {$\N$};
      }
    \end{tikzpicture}
    \caption{\label{fig:reduction}}
  \end{figure}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_2)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_1, \nu_2)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_1, \nu_2)$-edge $e = (a, a')$ in $\mathcal{M}$.
    Under this assumption, we show that $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Indeed, suppose, aiming at a contradiction,
    that there exists a $(\nu_1, \nu_1)$-edge $(x, x')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free,
    we must have $x < a$.
    Then it follows that $\mu(x) < \mu(a)$ (since $\nu_1$ is increasing) and
    $\mu(x') > \mu(a')$ (since $\nu_1$ is above $\nu_2$),
    which contradicts our hypothesis.
    Hence $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Furthermore, since $\nu_1$ is increasing and
    there exists only one $(\nu_1, \nu_2)$-edge $(a, a')$ in $\mathcal{M}$,
    we conclude that
    $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges.
    But $|\nu_1| = |\nu'_1| = N_1$ and $\mathcal{M}$ is perfect,
    and hence there exists a position, say $y$, in $\nu'_1$ that is
    not involved in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    We rule out this configuration by considering two cases:
    \begin{itemize}
      \item Position $y$ is involved in a $(\nu_2, \nu'_1)$-edge,
      say $(y', y)$. Then, we have $\mu(a) > \mu(y')$ (since $\nu_1$ is above $\nu_2$)
      and $\mu(a') < \mu(y)$ (since $\nu_2$ is below $\nu'_1$),
      which contradicts our hypothesis.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 1}.
      \item Position $y$ is not involved in a $(\nu_2, \nu'_1)$-edge.
      Since $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges
      in $\mathcal{M}$ and $|\nu'_1| = N_1$, there exists an edge $(y, y'')$ in $\mathcal{M}$
      that is neither a $(\nu_1, \nu'_1)$-edge nor a $(\nu_2, \nu'_1)$-edge
      nor a $(\nu'_1, \nu'_1)$-edge.
      In other words, $y'' > 2N_1 + N_2$.
      Now, for any $(\nu_1, \nu'_1)$-edge $(x, x')$ in $\mathcal{M}$, we
      have $\mu(x) < \mu(y)$ (since $\nu_1$ is below $\nu'_1$)
      and $\mu(x') > \mu(y'')$ (since $\nu'_1$ is above any other gadget),
      which contradicts our hypothesis.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 2}.
    \end{itemize}
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:one (nu_1, nu'_1)-edge}
    There is at least one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:one (nu_1, nu'_1)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then it follows that there exists an edge $(x, x')$ in $\mathcal{M}$,
    $1 \leq x \leq N_1$, that is neither a
    $(\nu_1, \nu_1)$-edge (since $N_1$ is odd)
    nor a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_1, \nu'_1)$ (by our contradiction hypothesis).
    (In other words, $x \leq N_1$ and $x' > 2N_1 + N_2$.)
    Therefore, since $\mathcal{M}$ is containment-free,
    there is neither a $(\nu_2, \nu_2)$-edge nor a $(\nu'_1, \nu'_1)$-edge
    in $\mathcal{M}$.
    Then it follows that every position $y$ of $\nu'_1$
    (\emph{i.e.}, $N_1+N_2 < y \leq 2N_1+N_2$)
    is involved in an edge $(y, y'$ of $\mathcal{M}$ with $y' \geq 2N_1+N_2$
    (otherwise $\mathcal{M}$ would not be containment-free).
    But $|\nu'_1| = N_1 = 2(2N_2 + 2n_3 + 2N_4 + 2n + 2k + 4) + 1
    > 2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4$, and hence at least one
    position in $\nu'_1$ can not be involved in an edge in $\mathcal{M}$.
    Then it follows that $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_2)-edge}]
  Combine Claim~\ref{claim:one (nu_1, nu'_1)-edge} with
  the fact that $\mathcal{M}$ is containment-free.
  \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu'_1)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_2, \nu'_1)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_2, \nu'_1)$-edge $e = (a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge}, there exists at least
    one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Furtheremore, since
    there is no $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge}),
    every position in $\nu_1$ is involved either in a
    $(\nu_1, \nu_1)$-edge or in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$
    (otherwise $\mathcal{M}$ would not be containment-free).
    Then it follows that that there is an odd number of $(\nu_1, \nu'_1)$-edges
    in $\mathcal{M}$ since $\mathcal{M}$ is perfect and $|\nu_1| = N_1$ is odd.
    Combining this with the fact that there exists exactly one $(\nu_2, \nu'_1)$-edge
    in $\mathcal{M}$ and $|\nu'_1| = N_1$ is odd,
    we conclude that there exists a position, say $x$, in $\nu'_1$
    that is neither involved in a $(\nu_1, \nu'_1)$-edge nor a $(\nu_1, \nu'_1)$-edge
    nor a $(\nu'_1, \nu'_1)$-edge.
    Write $(x, x')$, $N_1+N_2 < x \leq 2N_1 + N_2$ and $x' > 2N_1 + N_2$, this edge.
    We have $\mu(a) < \mu(x)$ (since $\nu_2$ is below $\nu'_1$)
    and $\mu(a') > \mu(x')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:one (nu_2, nu'_2)-edge}
    There is at least one $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

>>>>

\begin{proof}[of Lemma~\ref{lemma:at most one edge monotone}]
  \begin{figure}[t!]
    \centering
    \subfigure[%
      An increasing pattern before and above a decreasing pattern.
    ]{%
      \begin{tikzpicture}
        [
          scale=0.45,
          label/.style={anchor=base}
        ]
        % increasing pattern
        \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,5.8) grid (5.2,11.2);
        \foreach \x/\y in {0/6,1/7,2/8,3/9,4/10,5/11} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % decreasing pattern
        \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,-0.2) grid (11.2,5.2);
        \foreach \x/\y in {6/5,7/4,8/3,9/2,10/1,11/0} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % labels
        \node [label] (a) at (1,5) {$a$};
        \node [label] (b) at (4,5) {$b$};
        \node [label] (ap) at (7,-1) {$a'$};
        \node [label] (bp) at (10,-1) {$b'$};
        \node (nu1) at (2.5,4) {$\sigma_1$};
        \node (nu2) at (8.5,-2) {$\sigma_2$};
        % crossings edges
        \draw [line width=1pt]
        (1,7) .. controls +(0,12) and +(0,10) .. (7,4);
        \draw [line width=1pt]
        (4,10) .. controls +(0,12) and +(0,10) .. (10,1);
      \end{tikzpicture}
      \label{subfig:increasing before and aboce decreasing}
    }% end subfigure
    \qquad
    \subfigure[%
      A decreasing pattern before and below an increasing pattern.
    ]{%
    \begin{tikzpicture}
      [
        scale=0.45,
        label/.style={anchor=base}
      ]
      % decreasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,-0.2) grid (5.2,5.2);
      \foreach \x/\y in {0/5,1/4,2/3,3/2,4/1,5/0} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % decreasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,5.8) grid (11.2,11.2);
      \foreach \x/\y in {6/6,7/7,8/8,9/9,10/10,11/11} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % labels
      \node [label] (a) at (1,-1) {$a$};
      \node [label] (b) at (4,-1) {$b$};
      \node [label] (ap) at (7,5) {$a'$};
      \node [label] (bp) at (10,5) {$b'$};
      \node (nu1) at (2.5,-2) {$\sigma_1$};
      \node (nu2) at (8.5,4) {$\sigma_2$};
      % crossings edges
      \draw [line width=1pt]
      (1,4) .. controls +(0,10) and +(0,12) .. (7,7);
      \draw [line width=1pt]
      (4,1) .. controls +(0,10) and +(0,12) .. (10,10);
      \end{tikzpicture}
      \label{subfig:decresing before and below increasing}
    }% end subfigure
    \caption{\label{fig:subfig:no (nu_1, nu_2)-edge}%
      Lemma~\ref{lemma:at most one edge monotone}:
      Assuming a $(\nu_1,\nu_2)$-edge $(a, b)$ in $\mathcal{M}$.
    }
  \end{figure}
  We first prove \emph{1}.
  Suppose, aiming at a contradiction, that there exist two
  $(\sigma_1, \sigma_2)$-edges $(a, a')$ and $(b, b')$ in $\mathcal{M}$.
  Since $\mathcal{M}$ is containment-free, we may assume $a < b$ and $a' < b'$.
  Therefore, we have
  $\pi(a) < \pi(b)$ (since $\sigma_1$ is increasing) and
  $\pi(a') > \pi(b')$ (since $\sigma_2$ is decreasing),
  which contradicts our hypothesis about $\mathcal{M}$.

  As for \emph{2}, suppose, still aiming at a contradiction,
  that there exist two
  $(\sigma_1, \sigma_2)$-edges $(a, a')$ and $(b, b')$ in $\mathcal{M}$.
  Since $\mathcal{M}$ is containment-free, we may assume $a < b$ and $a' < b'$.
  Therefore, we have
  $\pi(a) > \pi(b)$ (since $\sigma_1$ is decreasing) and
  $\pi(a') < \pi(b')$ (since $\sigma_2$ is increasing),
  which contradicts our hypothesis about $\mathcal{M}$.
  \qed
\end{proof}

@@

    \begin{tikzpicture}[
      scale=.95,
      >=stealth',
      shorten >=1pt,
      main node/.style={align=center},
      cell/.style={draw,ultra thick,fill=black!5},
      structure link/.style={line width=1.5pt},
      pattern link/.style={line width=1.5pt,black!20},
      monotone/.style={->,thick}
      % edges
      % pi 1 - pi 2
      \draw [pattern link] (8.5,6) .. controls +(0,1) and +(0,2) .. (10.5,5);
      % pi 2 - sigma 2
      \draw [pattern link] (10.5,5) .. controls +(0,1) and +(0,3) .. (11.5,4);
      % 1
      \draw [structure link] (0.5,11) .. controls +(0,2) and +(0,1) .. (2.5,12);
      \node (claim edge 1) at (1.5,13.5) {Claim~\ref{claim:(nu_1, nu'_1)-edge}};
      \node (claim edge 1) at (1.5,13) {Claim~\ref{claim:all (nu_1, nu'_1)-edges}};
      % 2
      \draw [structure link] (1.5,2) .. controls +(0,1) and +(0,3) .. (6.5,1);
      \node (claim edge 2) at (4,4) {Claim\ref{claim:(nu_2, nu'_2)-edge}};
      \node (claim edge 2) at (4,3.5) {Claim\ref{claim:all (nu_2, nu'_2)-edges}};
      % 3
      \draw [structure link] (3.5,9) .. controls +(0,3) and +(0,1.5) .. (7.5,10);
      \node (claim edge 1) at (5.5,11.5) {Claim\ref{claim:(nu_3, nu'_3)-edge}};
      % 4
      \draw [structure link] (5.5,8) .. controls +(0,1) and +(0,7) .. (9.5,3);
      \node (claim edge 1) at (8.5,8.5) {Claim\ref{}};
      % sigma 1 - pi 1
      \draw [structure link] (4.5,6) .. controls +(0,-2) and +(0,-1) .. (8.5,5);
      \node (claim edge 1) at (6.5,4) {Claim\ref{}};
      % nodes
      % 1
      \draw [cell] (0,10) -- (1,10) -- (1,11) -- (0,11) -- cycle;
      \draw [monotone] (0,10) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu_1$};
      %\draw [draw,ultra thick,fill=black!5] (0,10) -- (1,10) -- (1,11) -- (0,11) -- cycle;
      \draw [cell] (2,11) -- (3,11) -- (3,12) -- (2,12) -- cycle;
      \draw [monotone] (2,11) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu'_1$};
      % 2
      \draw [cell] (1,1) -- (2,1) -- (2,2) -- (1,2) -- cycle;
      \draw [monotone] (1,2) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu_2$};
      \draw [cell] (6,0) -- (7,0) -- (7,1) -- (6,1) -- cycle;
      \draw [monotone] (6,1) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu'_2$};
      % 3
      \draw [cell] (3,8) -- (4,8) -- (4,9) -- (3,9) -- cycle;
      \draw [monotone] (3,8) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu_3$};
      \draw [cell] (7,9) -- (8,9) -- (8,10) -- (7,10) -- cycle;
      \draw [monotone] (7,9) -- ++(1,1) node [midway,fill=white,fill=black!5] {$\nu'_3$};
      % 4
      \draw [cell] (5,7) -- (6,7) -- (6,8) -- (5,8) -- cycle;
      \draw [monotone] (5,8) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu_4$};
      \draw [cell] (9,2) -- (10,2) -- (10,3) -- (9,3) -- cycle;
      \draw [monotone] (9,3) -- ++(1,-1) node [midway,fill=white,fill=black!5] {$\nu'_4$};
      % sigma 1
      \draw [cell] (4,6) -- (5,6) -- (5,7) -- (4,7) -- cycle;
      \node [main node] (sigma1) at (4.5,6.5) {$\sigma'$};
      % pi 1
      \draw [cell] (8,5) -- (9,5) -- (9,6) -- (8,6) -- cycle;
      \node [main node] (pi1) at (8.5,5.5) {$\pi'$};
      % pi 2
      \draw [cell] (10,4) -- (11,4) -- (11,5) -- (10,5) -- cycle;
      \node [main node] (sigma2) at (10.5,4.5) {$\pi''$};
      % sigma 2
      \draw [cell] (11,3) -- (12,3) -- (12,4) -- (11,4) -- cycle;
      \node [main node] (pi2) at (11.5,3.5) {$\sigma''$};
      % grid
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (0,0) grid (12,12);
      % row size
      \foreach \y/\N in {0.5/N_2,1.5/N_2,2.5/N_4,3.5/k,4.5/n,5.5/n+2,6.5/k+2,7.5/N_4,8.5/N_3,9.5/N_3,10.5/N_1,11.4/N_1} {
          \node at (-0.5,\y) (R\y) {$\N$};
      % column size
      \foreach \x/\N in
      {0.5/N_1,1.5/N_2,2.5/N_1,3.5/N_3,4.5/k+2,5.5/N_4,6.5/N_2,7.5/N_3,8.5/n+2,9.5/N_4,10.5/n,11.5/k} {
          \node at (\x,-0.5) (C\x) {$\N$};
    \caption{\label{fig:reduction}}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_2)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_1, \nu_2)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_1, \nu_2)$-edge $e = (a, a')$ in $\mathcal{M}$.
    Under this assumption, we show that $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Indeed, suppose, aiming at a contradiction,
    that there exists a $(\nu_1, \nu_1)$-edge $(x, x')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free,
    we must have $x < a$.
    Then it follows that $\mu(x) < \mu(a)$ (since $\nu_1$ is increasing) and
    $\mu(x') > \mu(a')$ (since $\nu_1$ is above $\nu_2$),
    which contradicts our hypothesis about $\mathcal{M}$.
    Hence $\mathcal{M}$ does not contain any $(\nu_1, \nu_1)$-edge.
    Furthermore, since $\nu_1$ is increasing and
    there exists only one $(\nu_1, \nu_2)$-edge $(a, a')$ in $\mathcal{M}$,
    we conclude that
    $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges.
    But $|\nu_1| = |\nu'_1| = N_1$ and $\mathcal{M}$ is perfect,
    and hence there exists a position, say $y$, in $\nu'_1$ that is
    not involved in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    We rule out this configuration by considering two cases:
    \begin{itemize}
      \item Position $y$ is involved in a $(\nu_2, \nu'_1)$-edge,
      say $(y', y)$. Then, we have $\mu(a) > \mu(y')$ (since $\nu_1$ is above $\nu_2$)
      and $\mu(a') < \mu(y)$ (since $\nu_2$ is below $\nu'_1$),
      which contradicts our hypothesis about $\mathcal{M}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 1}.
      \item Position $y$ is not involved in a $(\nu_2, \nu'_1)$-edge.
      Since $\mathcal{M}$ contains $N_1-1$ pairwise crossing $(\nu_1, \nu'_1)$-edges
      in $\mathcal{M}$ and $|\nu'_1| = N_1$, there exists an edge $(y, y'')$ in $\mathcal{M}$
      that is neither a $(\nu_1, \nu'_1)$-edge nor a $(\nu_2, \nu'_1)$-edge
      nor a $(\nu'_1, \nu'_1)$-edge.
      In other words, $y'' > 2N_1 + N_2$.
      Now, for any $(\nu_1, \nu'_1)$-edge $(x, x')$ in $\mathcal{M}$, we
      have $\mu(x) < \mu(y)$ (since $\nu_1$ is below $\nu'_1$)
      and $\mu(x') > \mu(y'')$ (since $\nu'_1$ is above any other gadget),
      which contradicts our hypothesis about $\mathcal{M}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 2}.
    \end{itemize}
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:(nu_1, nu'_1)-edge}
    There is at least one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:(nu_1, nu'_1)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then it follows that there exists an edge $(x, x')$ in $\mathcal{M}$,
    $1 \leq x \leq N_1$, that is neither a
    $(\nu_1, \nu_1)$-edge (since $N_1$ is odd)
    nor a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_1, \nu'_1)$ (by our contradiction hypothesis).
    (In other words, $x \leq N_1$ and $x' > 2N_1 + N_2$.)
    Therefore, since $\mathcal{M}$ is containment-free,
    there is neither a $(\nu_2, \nu_2)$-edge nor a $(\nu'_1, \nu'_1)$-edge
    in $\mathcal{M}$.
    Then it follows that every position $y$ of $\nu'_1$
    (\emph{i.e.}, $N_1+N_2 < y \leq 2N_1+N_2$)
    is involved in an edge $(y, y'$ of $\mathcal{M}$ with $y' \geq 2N_1+N_2$
    (otherwise $\mathcal{M}$ would not be containment-free).
    But $|\nu'_1| = N_1 = 2(2N_2 + 2n_3 + 2N_4 + 2n + 2k + 4) + 1
    > 2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4$, and hence at least one
    position in $\nu'_1$ can not be involved in an edge in $\mathcal{M}$.
    Then it follows that $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

  The above claim will be complement in upcoming Claim~\ref{claim: all (nu_1, nu'_1)-edges}.

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_2)-edge}]
  Combine Claim~\ref{claim:(nu_1, nu'_1)-edge} with
  the fact that $\mathcal{M}$ is containment-free.
  \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu'_1)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_2, \nu'_1)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_2, \nu'_1)$-edge $e = (a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge}, there exists at least
    one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Furtheremore, since
    there is no $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge}),
    every position in $\nu_1$ is involved either in a
    $(\nu_1, \nu_1)$-edge or in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$
    (otherwise $\mathcal{M}$ would not be containment-free).
    Then it follows that that there is an odd number of $(\nu_1, \nu'_1)$-edges
    in $\mathcal{M}$ since $\mathcal{M}$ is perfect and $|\nu_1| = N_1$ is odd.
    Combining this with the fact that there exists exactly one $(\nu_2, \nu'_1)$-edge
    in $\mathcal{M}$ and $|\nu'_1| = N_1$ is odd,
    we conclude that there exists a position, say $x$, in $\nu'_1$
    that is neither involved in a $(\nu_1, \nu'_1)$-edge nor a $(\nu_1, \nu'_1)$-edge
    nor a $(\nu'_1, \nu'_1)$-edge.
    Write $(x, x')$, $N_1+N_2 < x \leq 2N_1 + N_2$ and $x' > 2N_1 + N_2$, this edge.
    We have $\mu(a) < \mu(x)$ (since $\nu_2$ is below $\nu'_1$)
    and $\mu(a') > \mu(x')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:(nu_2, nu'_2)-edge}
    There is at least one $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:(nu_2, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is no
    $(\nu_2, \nu'_2)$-edge in $\mathcal{M}$.
    Notice that there is neither
    a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_2, \nu_2)$-edge (Claim~\ref{claim:no (nu_2, nu_2)-edge})
    nor a $(\nu_2, \nu'_1)$-edge (Claim~\ref{claim:no (nu_2, nu'_1)-edge})
    in $\mathcal{M}$.
    But $|\nu_2| = N_2 > 2N_3 + 2N_4 + 2n + 2k +4$.
    Hence $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}
